From Real-time Attention Assessment to ``With-me-ness'' in Human-Robot Interaction

### 2015-09-24 paper.tex
Updated all the results
Agreement is now correctly reported with a Cohen Kappa, and uses the 'raw' data computed by the robot

Successful detection of the head, and, when detected, the attentional target of
the children as estimated by the robot, were logged during the experiment (in
total, $6\times19.6=117.6$ min of interaction).\fixme{What it the case that 2
focuses of attention were sometimes detected? what did we do in such a
case?}

@@

    \begin{tabular}{p{5.5cm}cccccccc}
        \toprule
        {\bf Subject} & 1 & 2 & 3 & 4 & 5 & 6 & {\bf M} & {\it SD} \\
        \midrule
        {\bf Head pose tracking} (\%) & 88.2 & 83.5 & 90.5 & 83.1 & 87.9 & 85.0 & {\bf 86.4} & {\it 3.0} \\ 
        \midrule
        {\bf Agreement} (\%) & 61.1 & 85.5 & 80.8 & 62.2 & 63.4 & 83.9 & {\bf 72.8} & {\it 11.7}\\
        {\bf Cronbach's $\alpha$} & 0.63 & 0.81 & 0.82 & 0.59 & 0.64 & 0.78 & {\bf0.71} & {\it0.10}\\
        %{\bf Cosine affinity} & 0.73 & 0.82 & 0.87 & 0.73 & 0.77 & 0.89 & {\bf 0.8} & {\it 0.07} \\
        \bottomrule
    \end{tabular}
    \label{tab:results}
\end{table*}

@@

\begin{table}[h!]
    \centering
    \caption{\textbf{Levels of with-me-ness}. For each subject, the with-me-ness
    level is reported over the whole interaction, either based on the
    ground-truth (\ie \emph{ground-truth with-me-ness}), or based on the focus of
    attention measured by the robot.}

    \begin{tabular}{p{1cm}cccccccc}
        \toprule
        Subject & 1 & 2 & 3 & 4 & 5 & 6 & {\bf M} & {\it SD} \\
        \midrule
        $\mathcal{W}_{g.truth}$ & 92.6 & 88.8  & 95.8 & 93.1 & 96.5 & 89.6 & {\bf 92.7} & {\it 3.1} \\ 
        $\mathcal{W}_{robot}$ & 89.6 & 84.4 & 86.6 & 72.8 & 81.9 & 79.7 & {\bf 82.5} & {\it 5.4} \\
        \bottomrule
    \end{tabular}
    \label{tab:results-with-me-ness}
\end{table}

>>>>

Successful detections of the head, and, when detected, the attentional targets of
the children as estimated by the robot, were logged during the experiment (in
total, $6\times19.6=117.6$ min of interaction). The only post-processing
consisted in filtering out gaze shifts (short episodes -- below 500ms -- between
two attentional targets).

@@

    \begin{tabular}{p{5.5cm}cccccccc}
        \toprule
        {\bf Subject} & 1 & 2 & 3 & 4 & 5 & 6 & {\bf M} & {\it SD} \\
        \midrule
        {\bf Head pose tracking} (\%) & 88.2 & 83.5 & 90.5 & 83.1 & 87.9 & 85.0 & {\bf 86.4} & {\it 3.0} \\ 
        \midrule
        {\bf Agreement} (\%) & 58.9 & 67.1 & 79.2 & 48.3 & 65 & 77.1 & {\bf 65.9} & {\it 11.5}\\
        {\bf Cohen's $\kappa$} & 0.48 & 0.56 & 0.68 & 0.26 & 0.47 & 0.68 & {\bf 0.52} & {\it 0.16}\\
        %{\bf Cosine affinity} & 0.73 & 0.82 & 0.87 & 0.73 & 0.77 & 0.89 & {\bf 0.8} & {\it 0.07} \\
        \bottomrule
    \end{tabular}
    \label{tab:results}
\end{table*}

@@

\begin{table}[h!]
    \centering
    \caption{\textbf{Levels of with-me-ness}. For each subject, the with-me-ness
    level is reported over the whole interaction, either based on the
    ground-truth (\ie \emph{ground-truth with-me-ness}), or based on the focus of
    attention measured by the robot. $\mathcal{W}_{robot}$ is strongly correlated to
    $\mathcal{W}_{groundtruth}$: Pearson's $r(4)=0.50$.}

    \begin{tabular}{p{1cm}cccccccc}
        \toprule
        Subject & 1 & 2 & 3 & 4 & 5 & 6 & {\bf M} & {\it SD} \\
        \midrule
        $\mathcal{W}_{g.truth}$ & 79.3 & 82.6  & 90.5 & 87.9 & 90.7 & 83.6 & {\bf 85.8} & {\it 4.6} \\ 
        $\mathcal{W}_{robot}$ & 52.5 & 55.5 & 74.1 & 52.6 & 60.0 & 66.4 & {\bf 60.2} & {\it 8.6} \\
        \bottomrule
    \end{tabular}
    \label{tab:results-with-me-ness}
\end{table}
